Compiling refinement types to dependent types

### 2020-07-20 tex/paper.tex
State the functions are total

\newtheorem{theorem}{Theorem}

@@

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

Having defined these functions, we formulate a simple but useful lemma:
\begin{lemma}[Translation totality]
  $\Tranctx$, $\Tranty$ and $\Tranterm$ are total.
\end{lemma}
\begin{proof}
  Firstly, each function is defined for all possible inputs.
  Then, each function recurses on structurally smaller inputs,
  and, since derivation trees are finite,
  this implies each function terminates for any input.
\end{proof}
